Mapping Mixtures of Genotype-by-Weather Interactions in Switchgrass (Panicum virgatum)

### 2024-01-18 manuscript/revision2/revision2.qmd
manuscript: AHM revisions to Figure 3 and 4 and some M&M citation work

Our analysis of the timing of flowering showed that the Gulf and Midwest subpopulations have distinct GxWeather: flowering timing in the Midwest subpopulation has photoperiod-related variation, in that flowering timing covaries with a day length change signal in the two days before flowering occurs. In contrast, the Gulf subpopulation does not have variation in flowering based on photoperiod. Instead, the Gulf subpopulation has variation in flowering that covaries with the rainfall that occurs in the week prior to flowering. The genomic regions affecting flowering that we re-estimated across all eight sites were also supported by QTL from an independent mapping population at these sites (\@fig-qtl C).

Identifying the environmental cues that are predictive of, or even correlated with, plant phenotypic responses remains a major challenge to studies interrogating gene action across many natural environments. Clearly, the photoperiod and cumulative GDD cues we identify here are functions of the genotypes measured, are not predictive, and capture only a minority of SNP effects on flowering. We know still less about the overwintering parameters that affect green-up, which is reflected in our lower ability to assign SNP effects on green-up to weather-based cues. More generally, it is difficult to predict the time scales over which individuals may integrate environmental cues, particularly in perennial species which may integrate these cues over longer time scales. Mash offers an opportunity to specify multiple environmental cues and compete them to explain patterns of SNP effects, allowing us to detect how important these cues are genome-wide, and how strongly each cue influences each SNP. This is a key development to further improve our understanding of genetic variation in GxE.

@@

![Caption for this figure...](images/Figure_2_Covariance_matrices_and_posterior_weights.png){#fig-covar}

@@

In 2019, we scored two phenological events every two days in two mapping populations of switchgrass, a diversity panel and a pseudo-F2 cross, planted at eight common garden locations (32, 34, 37). We scored green-up date as the day of the year when 50% of the tiller area of the crown of the plant cut the previous year had green growth. Flowering date was the day of the year when 50% of the plant tillers had panicles undergoing anthesis. We scored green-up and flowering as day of the year, then linked these dates to multiple weather-based environmental factors measured daily at each common garden (SI Appendix, Section S1, Table S1).

The formation and resequencing of the diversity panel has been described previously (32). The diversity panel contained 134 sequenced, clonally propagated individuals from the Midwest genetic subpopulation, and 229 from the Gulf genetic subpopulation. To allow for the possibility that different subpopulations had different strengths of connection between our phenotypes and genotypes (38), we conducted three sets of genetic analyses: on Gulf and Midwest genotypes separately, and on both subpopulations together ('Both'). Analyses to determine narrow-sense heritability (h2) for green-up and flowering were done using linear mixed models and followed (32). Details on these models can be found in (SI Appendix, Section S3,S4).

@@

To evaluate the prevalence and kinds of covariance patterns of SNP effects across our common gardens, we used multivariate adaptive shrinkage (mash) on SNP effect estimates from the diversity panel (35). Mash is a statistical method that allows estimation and comparison of many effects jointly across many different conditions; it improves on previous methods by allowing multiple, arbitrary correlations in effect sizes among conditions (SI Appendix, Section S5). To obtain SNP effect estimates, we first conducted univariate genome-wide association at each common garden for green-up and flowering date. We then analyzed SNP effects for the top 19K relatively unlinked (r2 \< 0.2) SNPs per condition using mash, as in (32). Details on these models can be found in (SI Appendix, Section S6).

We generated hypothesis-based covariance matrices derived from correlations in environmental cues in the green-up or flowering date windows for the three subpopulations (SI Appendix, Table S1, Section S1). These covariance matrices represent correlations between identical genotypes drawn from a specific population at pairs of common gardens; covariances near one mean that the population has a strong, positive linear relationship in individual responses at that pair of gardens, while covariances near zero mean that there is no relationship within the population for individual responses at that pair of gardens. Mash SNP effects will undergo strong shrinkage towards one another in the first case, and little shrinkage in the second case. Mash also generates data-driven covariance matrices corresponding to major patterns of SNP effects present in the data. We generated six data-driven matrices per mash run, five (denoted DD_PCA_1 through DD_PCA_5) produced by singular value decomposition (SVD) of an overall matrix, denoted 'DD_tPCA'. We used SVD to present vectors of garden-specific effects for each numbered DD_PCA matrix, because the first eigenvector of a SVD explains 100% of the variation in these matrices, and each value in this eigenvector represents one garden-specific effect.

@@

Using the lfsr rather than the local false discovery rate (lfdr) is a critical change in our ability to detect antagonistic pleiotropy. The lfdr, like other measures of FDR, focuses on if we have enough evidence to reject the null hypothesis that an effect j is 0 -- that there is a significant effect. Previous studies of antagonistic pleiotropy (e.g. (37)) have used the lfdr or equivalent statistical tests to detect antagonistic pleiotropy. These tests were conservative, in that they required two non-zero effects of different signs, while tests for differential sensitivity required only one non-zero effect. This previous work recognized that this testing bias could lead to undercounting occurrences of antagonistic pleiotropy (26, 27), and sought to reduce it by permutation (28). However, using the lfsr to test for antagonistic pleiotropy does not undercount occurrences of antagonistic pleiotropy, as this statistic answers a fundamentally different question. For each effect j, the lfsr_j is defined as the probability that we make an error in the sign of effect j if we were forced to declare the effect positive or negative (Stephens paper). Thus, rather than asking "Are these two effects different?" - as we reasonably expect two effects to be, even if this difference cannot be measured - the local false sign rate answers a more meaningful question: Can we be confident in the sign of this effect?

In addition, the get_GxE function also sets an arbitrary threshold to count an effect as changing in magnitude between environments, commonly known as differential sensitivity. For differential sensitivity, this function determines if effects significant in both conditions are of the same sign and of a magnitude (not tested for significance) that differs by a factor of 0.4 or more. The remaining effects that are significant in both conditions have the same effect sign and similar effect magnitudes and we denote these effects as having no GxE. The distinction between effects with different magnitudes is arbitrary but useful to fully characterize how effects vary across environments. and our use of the lfsr to determine significance and our specification that SNP effects must be significant in both conditions to be included means that our tests for antagonistic pleiotropy carry an equal statistical burden to those measuring differential sensitivity and effects without GxE.

>>>>

Our analysis of the timing of flowering showed that the Gulf and Midwest subpopulations have distinct GxWeather: flowering timing in the Midwest subpopulation has photoperiod-related variation, in that flowering timing covaries with a day length change signal two days before flowering occurs. In contrast, the Gulf subpopulation does not have variation in flowering based on a photoperiod cue. Instead, the Gulf subpopulation has variation in flowering that covaries with the rainfall that occurs in the week prior to flowering. The genomic regions affecting flowering that we re-estimated across all eight sites were also supported by QTL from an independent mapping population at these sites (\@fig-qtl C).

Identifying the environmental cues that are predictive of, or even correlated with, plant phenotypic responses remains a major challenge to studies interrogating gene action across many natural environments. The GxWeather photoperiod and cumulative rainfall cues we identify here are functions of the genotypes measured and capture only a minority of SNP effects on flowering. We know still less about the overwintering parameters that cause variation in the start of vegetative. Though we could assign SNP effects to a GxWeather covariance structure in the Gulf subpopulation, we could not do this for the Midwest subpopulation. More generally, it is difficult to predict the time scales over which individuals may integrate environmental cues, particularly in perennial species which may integrate these cues over longer time scales. If this integration time itself varies between individuals, we cannot select a covariance structure that reflects this, though these structures would likely be highly correlated with GxWeather structures we did include. Mash offers an opportunity to specify multiple environmental cues and compete them to explain patterns of genetic effects, allowing us to detect how important these cues are genome-wide, and how strongly each cue influences each SNP. This is a key development to further improve our understanding of genetic variation in GxE.

@@

![Caption for this figure... blah blah blah.](images/Figure_2_Covariance_matrices_and_posterior_weights.png){#fig-covar}

![Comparisons of pairs of jointly re-estimated effects across eight gardens, for effects with lfsr \< 0.05. AHM is considering moving this figure to the supplement and substantially simplifying the figure in the main text, perhaps just showing total effects in Texas, the North, and maybe Oklahoma. Essentially making Table 2 into a new, simplified figure. ](images/Figure_3_Effect_Types_by_Site.png){#fig-effects}

![SNP effects for SNPs within QTL. AHM to re-make this figure now LZ has re-run the QTL analysis, the assmption being the re-analysis will not change the figure or the text much. The bigger question for TEJ and AH is whether we want to keep this analysis in the paper, what does it add?](images/Figure_4_mash_SNP_effects.png){#fig-qtl}

@@

In 2019, we scored two phenological events every two days in two mapping populations of switchgrass, a diversity panel and a pseudo-F2 cross, planted at eight common garden locations (32, 34, 37). We scored the start of vegetative growth as the day of the year when 50% of the tiller area of the crown of the plant cut the previous year had green growth. The start of reproductive growth, or flowering date, was the day of the year when 50% of the plant tillers had panicles undergoing anthesis. We scored green-up and flowering as day of the year, then linked these dates to multiple weather-based environmental factors measured daily at each common garden (SI Appendix, Section S1, Table S1).

The formation and resequencing of the diversity panel has been described previously @lovell2021genomic. The diversity panel contained 134 sequenced, clonally propagated individuals from the Midwest genetic subpopulation, and 229 from the Gulf genetic subpopulation. To allow for the possibility that different subpopulations had different strengths of connection between our phenotypes and genotypes (38), we conducted three sets of genetic analyses: on Gulf and Midwest genotypes separately, and on both subpopulations together ('Both'). Analyses to determine narrow-sense heritability (h^2^) for green-up and flowering were done using linear mixed models and followed @lovell2021genomic. Details on these models can be found in (SI Appendix, Section S3,S4).

@@

To evaluate the prevalence and kinds of covariance patterns of SNP effects across our common gardens, we used multivariate adaptive shrinkage (*mash*) on SNP effect estimates from the diversity panel (35). Mash is a statistical method that allows estimation and comparison of many effects jointly across many different conditions; it improves on previous methods by allowing multiple, arbitrary correlations in effect sizes among conditions (SI Appendix, Section S5). To obtain SNP effect estimates, we first conducted univariate genome-wide association at each common garden for green-up and flowering date. We then analyzed SNP effects for the top 19K relatively unlinked (r^2^ \< 0.2) SNPs per condition using mash, as in @lovell2021genomic. Details on these models can be found in (SI Appendix, Section S6).

We generated hypothesis-based covariance matrices derived from correlations in environmental cues in the green-up or flowering date windows for the three populations (SI Appendix, Table S1, Section S1). These covariance matrices represent correlations between identical genotypes drawn from a specific population at pairs of common gardens; covariances near one mean that the population has a strong, positive linear relationship in individual responses at that pair of gardens, while covariances near zero mean that there is no relationship within the population for individual responses at that pair of gardens. Mash SNP effects will undergo strong shrinkage towards one another in the first case, and little shrinkage in the second case. Mash also generates data-driven covariance matrices corresponding to major patterns of SNP effects present in the data. We generated six data-driven matrices per mash run, five produced by singular value decomposition (SVD) of an overall matrix.

@@

Using the lfsr rather than the local false discovery rate (lfdr) is a critical change in our ability to detect antagonistic pleiotropy. The lfdr, like other measures of FDR, focuses on if we have enough evidence to reject the null hypothesis that an effect j is 0, or that there is a significant effect. Previous studies of antagonistic pleiotropy (e.g. (37)) have used the lfdr or equivalent statistical tests to detect antagonistic pleiotropy. These tests were conservative, in that they required two non-zero effects of different signs, while tests for differential sensitivity required only one non-zero effect. This previous work recognized that this testing bias could lead to undercounting occurrences of antagonistic pleiotropy (26, 27), and sought to reduce it by permutation (28). However, using the lfsr to test for antagonistic pleiotropy does not undercount occurrences of antagonistic pleiotropy, as this statistic answers a fundamentally different question. For each effect j, the lfsr~j~ is defined as the probability that we make an error in the sign of effect j if we were forced to declare the effect positive or negative @10.1093/biostatistics/kxw041. Thus, rather than asking "Are these two effects different?" - as we reasonably expect two effects to be, even if this difference cannot be measured - the local false sign rate answers a more meaningful question: Can we be confident in the sign of this effect?

In addition, the get_GxE function also sets an arbitrary threshold to count an effect as changing in magnitude between environments, commonly known as differential sensitivity or a change in amplitude of . For differential sensitivity, this function determines if effects significant in both conditions are of the same sign and of a magnitude (not tested for significance) that differs by a factor of 0.4 or more. The remaining effects that are significant in both conditions have the same effect sign and similar effect magnitudes and we denote these effects as having no GxE. The distinction between effects with different magnitudes is arbitrary but useful to fully characterize how effects vary across environments. and our use of the lfsr to determine significance and our specification that SNP effects must be significant in both conditions to be included means that our tests for antagonistic pleiotropy carry an equal statistical burden to those measuring differential sensitivity and effects without GxE.

### 2024-01-18 manuscript/revision2/revision2.tex
manuscript: AHM revisions to Figure 3 and 4 and some M&M citation work

Our analysis of the timing of flowering showed that the Gulf and Midwest
subpopulations have distinct GxWeather: flowering timing in the Midwest
subpopulation has photoperiod-related variation, in that flowering
timing covaries with a day length change signal in the two days before
flowering occurs. In contrast, the Gulf subpopulation does not have
variation in flowering based on photoperiod. Instead, the Gulf
subpopulation has variation in flowering that covaries with the rainfall
that occurs in the week prior to flowering. The genomic regions
affecting flowering that we re-estimated across all eight sites were
also supported by QTL from an independent mapping population at these
sites (@fig-qtl C).

Identifying the environmental cues that are predictive of, or even
correlated with, plant phenotypic responses remains a major challenge to
studies interrogating gene action across many natural environments.
Clearly, the photoperiod and cumulative GDD cues we identify here are
functions of the genotypes measured, are not predictive, and capture
only a minority of SNP effects on flowering. We know still less about
the overwintering parameters that affect green-up, which is reflected in
our lower ability to assign SNP effects on green-up to weather-based
cues. More generally, it is difficult to predict the time scales over
which individuals may integrate environmental cues, particularly in
perennial species which may integrate these cues over longer time
scales. Mash offers an opportunity to specify multiple environmental
cues and compete them to explain patterns of SNP effects, allowing us to
detect how important these cues are genome-wide, and how strongly each
cue influences each SNP. This is a key development to further improve
our understanding of genetic variation in GxE.

@@

\caption{\label{fig-covar}Caption for this figure\ldots{}}

@@

In 2019, we scored two phenological events every two days in two mapping
populations of switchgrass, a diversity panel and a pseudo-F2 cross,
planted at eight common garden locations (32, 34, 37). We scored
green-up date as the day of the year when 50\% of the tiller area of the
crown of the plant cut the previous year had green growth. Flowering
date was the day of the year when 50\% of the plant tillers had panicles
undergoing anthesis. We scored green-up and flowering as day of the
year, then linked these dates to multiple weather-based environmental
factors measured daily at each common garden (SI Appendix, Section S1,
Table S1).

The formation and resequencing of the diversity panel has been described
previously (32). The diversity panel contained 134 sequenced, clonally
propagated individuals from the Midwest genetic subpopulation, and 229
from the Gulf genetic subpopulation. To allow for the possibility that
different subpopulations had different strengths of connection between
our phenotypes and genotypes (38), we conducted three sets of genetic
analyses: on Gulf and Midwest genotypes separately, and on both
subpopulations together (`Both'). Analyses to determine narrow-sense
heritability (h2) for green-up and flowering were done using linear
mixed models and followed (32). Details on these models can be found in
(SI Appendix, Section S3,S4).

@@

To evaluate the prevalence and kinds of covariance patterns of SNP
effects across our common gardens, we used multivariate adaptive
shrinkage (mash) on SNP effect estimates from the diversity panel (35).
Mash is a statistical method that allows estimation and comparison of
many effects jointly across many different conditions; it improves on
previous methods by allowing multiple, arbitrary correlations in effect
sizes among conditions (SI Appendix, Section S5). To obtain SNP effect
estimates, we first conducted univariate genome-wide association at each
common garden for green-up and flowering date. We then analyzed SNP
effects for the top 19K relatively unlinked (r2 \textless{} 0.2) SNPs
per condition using mash, as in (32). Details on these models can be
found in (SI Appendix, Section S6).

We generated hypothesis-based covariance matrices derived from
correlations in environmental cues in the green-up or flowering date
windows for the three subpopulations (SI Appendix, Table S1, Section
S1). These covariance matrices represent correlations between identical
genotypes drawn from a specific population at pairs of common gardens;
covariances near one mean that the population has a strong, positive
linear relationship in individual responses at that pair of gardens,
while covariances near zero mean that there is no relationship within
the population for individual responses at that pair of gardens. Mash
SNP effects will undergo strong shrinkage towards one another in the
first case, and little shrinkage in the second case. Mash also generates
data-driven covariance matrices corresponding to major patterns of SNP
effects present in the data. We generated six data-driven matrices per
mash run, five (denoted DD\_PCA\_1 through DD\_PCA\_5) produced by
singular value decomposition (SVD) of an overall matrix, denoted
`DD\_tPCA'. We used SVD to present vectors of garden-specific effects
for each numbered DD\_PCA matrix, because the first eigenvector of a SVD
explains 100\% of the variation in these matrices, and each value in
this eigenvector represents one garden-specific effect.

@@

Using the lfsr rather than the local false discovery rate (lfdr) is a
critical change in our ability to detect antagonistic pleiotropy. The
lfdr, like other measures of FDR, focuses on if we have enough evidence
to reject the null hypothesis that an effect j is 0 -- that there is a
significant effect. Previous studies of antagonistic pleiotropy
(e.g.~(37)) have used the lfdr or equivalent statistical tests to detect
antagonistic pleiotropy. These tests were conservative, in that they
required two non-zero effects of different signs, while tests for
differential sensitivity required only one non-zero effect. This
previous work recognized that this testing bias could lead to
undercounting occurrences of antagonistic pleiotropy (26, 27), and
sought to reduce it by permutation (28). However, using the lfsr to test
for antagonistic pleiotropy does not undercount occurrences of
antagonistic pleiotropy, as this statistic answers a fundamentally
different question. For each effect j, the lfsr\_j is defined as the
probability that we make an error in the sign of effect j if we were
forced to declare the effect positive or negative (Stephens paper).
Thus, rather than asking ``Are these two effects different?'' - as we
reasonably expect two effects to be, even if this difference cannot be
measured - the local false sign rate answers a more meaningful question:
Can we be confident in the sign of this effect?

In addition, the get\_GxE function also sets an arbitrary threshold to
count an effect as changing in magnitude between environments, commonly
known as differential sensitivity. For differential sensitivity, this
function determines if effects significant in both conditions are of the
same sign and of a magnitude (not tested for significance) that differs
by a factor of 0.4 or more. The remaining effects that are significant
in both conditions have the same effect sign and similar effect
magnitudes and we denote these effects as having no GxE. The distinction
between effects with different magnitudes is arbitrary but useful to
fully characterize how effects vary across environments. and our use of
the lfsr to determine significance and our specification that SNP
effects must be significant in both conditions to be included means that
our tests for antagonistic pleiotropy carry an equal statistical burden
to those measuring differential sensitivity and effects without GxE.

>>>>

Our analysis of the timing of flowering showed that the Gulf and Midwest
subpopulations have distinct GxWeather: flowering timing in the Midwest
subpopulation has photoperiod-related variation, in that flowering
timing covaries with a day length change signal two days before
flowering occurs. In contrast, the Gulf subpopulation does not have
variation in flowering based on a photoperiod cue. Instead, the Gulf
subpopulation has variation in flowering that covaries with the rainfall
that occurs in the week prior to flowering. The genomic regions
affecting flowering that we re-estimated across all eight sites were
also supported by QTL from an independent mapping population at these
sites (@fig-qtl C).

Identifying the environmental cues that are predictive of, or even
correlated with, plant phenotypic responses remains a major challenge to
studies interrogating gene action across many natural environments. The
GxWeather photoperiod and cumulative rainfall cues we identify here are
functions of the genotypes measured and capture only a minority of SNP
effects on flowering. We know still less about the overwintering
parameters that cause variation in the start of vegetative. Though we
could assign SNP effects to a GxWeather covariance structure in the Gulf
subpopulation, we could not do this for the Midwest subpopulation. More
generally, it is difficult to predict the time scales over which
individuals may integrate environmental cues, particularly in perennial
species which may integrate these cues over longer time scales. If this
integration time itself varies between individuals, we cannot select a
covariance structure that reflects this, though these structures would
likely be highly correlated with GxWeather structures we did include.
Mash offers an opportunity to specify multiple environmental cues and
compete them to explain patterns of genetic effects, allowing us to
detect how important these cues are genome-wide, and how strongly each
cue influences each SNP. This is a key development to further improve
our understanding of genetic variation in GxE.

@@

\caption{\label{fig-covar}Caption for this figure\ldots{} blah blah
blah.}

\includegraphics{images/Figure_3_Effect_Types_by_Site.png}

\caption{\label{fig-effects}Comparisons of pairs of jointly re-estimated
effects across eight gardens, for effects with lfsr \textless{} 0.05.
AHM is considering moving this figure to the supplement and
substantially simplifying the figure in the main text, perhaps just
showing total effects in Texas, the North, and maybe Oklahoma.
Essentially making Table 2 into a new, simplified figure.}

\includegraphics{images/Figure_4_mash_SNP_effects.png}

\caption{\label{fig-qtl}SNP effects for SNPs within QTL. AHM to re-make
this figure now LZ has re-run the QTL analysis, the assmption being the
re-analysis will not change the figure or the text much. The bigger
question for TEJ and AH is whether we want to keep this analysis in the
paper, what does it add?}

@@

In 2019, we scored two phenological events every two days in two mapping
populations of switchgrass, a diversity panel and a pseudo-F2 cross,
planted at eight common garden locations (32, 34, 37). We scored the
start of vegetative growth as the day of the year when 50\% of the
tiller area of the crown of the plant cut the previous year had green
growth. The start of reproductive growth, or flowering date, was the day
of the year when 50\% of the plant tillers had panicles undergoing
anthesis. We scored green-up and flowering as day of the year, then
linked these dates to multiple weather-based environmental factors
measured daily at each common garden (SI Appendix, Section S1, Table
S1).

The formation and resequencing of the diversity panel has been described
previously (32). The diversity panel contained 134 sequenced, clonally
propagated individuals from the Midwest genetic subpopulation, and 229
from the Gulf genetic subpopulation. To allow for the possibility that
different subpopulations had different strengths of connection between
our phenotypes and genotypes (38), we conducted three sets of genetic
analyses: on Gulf and Midwest genotypes separately, and on both
subpopulations together (`Both'). Analyses to determine narrow-sense
heritability (h\textsuperscript{2}) for green-up and flowering were done
using linear mixed models and followed (32). Details on these models can
be found in (SI Appendix, Section S3,S4).

@@

To evaluate the prevalence and kinds of covariance patterns of SNP
effects across our common gardens, we used multivariate adaptive
shrinkage (\emph{mash}) on SNP effect estimates from the diversity panel
(35). Mash is a statistical method that allows estimation and comparison
of many effects jointly across many different conditions; it improves on
previous methods by allowing multiple, arbitrary correlations in effect
sizes among conditions (SI Appendix, Section S5). To obtain SNP effect
estimates, we first conducted univariate genome-wide association at each
common garden for green-up and flowering date. We then analyzed SNP
effects for the top 19K relatively unlinked (r\textsuperscript{2}
\textless{} 0.2) SNPs per condition using mash, as in (32). Details on
these models can be found in (SI Appendix, Section S6).

We generated hypothesis-based covariance matrices derived from
correlations in environmental cues in the green-up or flowering date
windows for the three populations (SI Appendix, Table S1, Section S1).
These covariance matrices represent correlations between identical
genotypes drawn from a specific population at pairs of common gardens;
covariances near one mean that the population has a strong, positive
linear relationship in individual responses at that pair of gardens,
while covariances near zero mean that there is no relationship within
the population for individual responses at that pair of gardens. Mash
SNP effects will undergo strong shrinkage towards one another in the
first case, and little shrinkage in the second case. Mash also generates
data-driven covariance matrices corresponding to major patterns of SNP
effects present in the data. We generated six data-driven matrices per
mash run, five produced by singular value decomposition (SVD) of an
overall matrix.

@@

Using the lfsr rather than the local false discovery rate (lfdr) is a
critical change in our ability to detect antagonistic pleiotropy. The
lfdr, like other measures of FDR, focuses on if we have enough evidence
to reject the null hypothesis that an effect j is 0, or that there is a
significant effect. Previous studies of antagonistic pleiotropy
(e.g.~(37)) have used the lfdr or equivalent statistical tests to detect
antagonistic pleiotropy. These tests were conservative, in that they
required two non-zero effects of different signs, while tests for
differential sensitivity required only one non-zero effect. This
previous work recognized that this testing bias could lead to
undercounting occurrences of antagonistic pleiotropy (26, 27), and
sought to reduce it by permutation (28). However, using the lfsr to test
for antagonistic pleiotropy does not undercount occurrences of
antagonistic pleiotropy, as this statistic answers a fundamentally
different question. For each effect j, the lfsr\textsubscript{j} is
defined as the probability that we make an error in the sign of effect j
if we were forced to declare the effect positive or negative (36). Thus,
rather than asking ``Are these two effects different?'' - as we
reasonably expect two effects to be, even if this difference cannot be
measured - the local false sign rate answers a more meaningful question:
Can we be confident in the sign of this effect?

In addition, the get\_GxE function also sets an arbitrary threshold to
count an effect as changing in magnitude between environments, commonly
known as differential sensitivity or a change in amplitude of . For
differential sensitivity, this function determines if effects
significant in both conditions are of the same sign and of a magnitude
(not tested for significance) that differs by a factor of 0.4 or more.
The remaining effects that are significant in both conditions have the
same effect sign and similar effect magnitudes and we denote these
effects as having no GxE. The distinction between effects with different
magnitudes is arbitrary but useful to fully characterize how effects
vary across environments. and our use of the lfsr to determine
significance and our specification that SNP effects must be significant
in both conditions to be included means that our tests for antagonistic
pleiotropy carry an equal statistical burden to those measuring
differential sensitivity and effects without GxE.
